Plug-and-play dual-tree algorithm runtime analysis

### 2015-08-25 bounds-files/general-runtime-bound.tex
Fix misstatement about reference recursions.

A reference recursion (lines
\ref{alg:line:ct-dual-ref-recursion-start}--\ref{alg:line:ct-dual-ref-recursion-end})
is similar to a query recursion, but the pruning strategy is significantly more
complicated.  Given $R$, we calculate $R_r$, which is the set of nodes in $R$
that have scale $s_r^{\max}$.  Then, for each node $\mathscr{N}_r$ in the set of
children of nodes in $R_r$, the node combinations $(\mathscr{N}_q,
\mathscr{N}_r)$ are scored and pruned if possible.  Those reference nodes that
were not pruned form the set $R'_{r - 1}$.  Then, this set is combined with $R
\setminus R_r$---that is, each of the nodes in $R$ that was {\em not} recursed
into---to produce $R'$, and the algorithm recurses with $\mathscr{N}_q$ and the
reference set $R'$.

>>>>

A reference recursion (lines
\ref{alg:line:ct-dual-ref-recursion-start}--\ref{alg:line:ct-dual-ref-recursion-end})
is similar to a query recursion, but the pruning strategy is significantly more
complicated.  Given $R$, we calculate $R_r$, which is the set of nodes in $R$
that have scale $s_r^{\max}$.  We expand each node in $R_r$ to construct $R_{r -
1}$: this is the set of children of all nodes in $R_r$.  This set is then
combined with $R \setminus R_r$ (that is, the set of references nodes not at
scale $s_r^{\max}$) to produce $R_{r - 1}$.  Each node in $R_{r - 1}$ is then
scored and pruned if possible, resulting in the pruned reference set $R'_{r -
1}$.  The algorithm then recurses with $\mathscr{N}_q$ and $R'_{r - 1}$.
